Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
updates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52686 72bbbca6-d526-0410-a7d9-f06f51895060

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

@@

\begin{table}
\begin{tabular}{ll}
 \textbf{Code switching}: & \\
\textbf{Quotations}: & And then he said ` ' \\
 \textbf{Named entities}: &``[Dr Jekyll] ha [Mr Hyde] embannet gant [Éditions Aber]'' \\
 \textbf{Interjections}: & ``Hey, that's great, [diolch yn fawr!]'' \\
 \textbf{Translations}: & ``Bloavezh mat d'an holl ! [Bonne année à tous !]'' \\
\end{tabular}
\label{table:examples}
\caption{Some examples of text segments containing more than one language}
\end{table}

>>>>

@@

\begin{table}
\begin{tabular}{ll}
 \textbf{Code switching}: & \\
\textbf{Quotations}: & And then he said ` ' \\
 \textbf{Named entities}: & [Dr Jekyll] ha [Mr Hyde] embannet gant [\'{E}ditions Aber] \\
 \textbf{Interjections}: & Hey, that's great, [diolch yn fawr!] \\
 \textbf{Translations}: & Bloavezh mat d'an holl ! [Bonne ann\'{e} \`{a} tous !] \\
\end{tabular}
\label{table:examples}
\caption{Some examples of text segments containing more than one language}
\end{table}
